---
title: "Homework 1"
author: Yujie Huang
output: html_document
date: "2022-09-24"
---


```{r, message = FALSE, warning = FALSE}
library (tidyverse)
```

## Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

```{r}
mean_flipper_length= mean(penguins$flipper_length_mm,na.rm = TRUE)  
```
A short description of the penguins dataset:
This is the penguins dataset. The important variables' names include species, island, bill_length_mm, bill_depth_mm, flipper_length_mm,body_mass_g, sex, and year. 
There are 344 rows and 8 columns in the dataset (344 observations of 8 variables). 
The mean flipper length = 200.92



```{r, warning = FALSE}
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm))+ geom_point(aes(color=species))

```

This is the scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable. 


```{r, warning = FALSE}
ggsave("first scatterplot_colored.pdf")
```



## Problem 2

```{r, message = FALSE, warning = FALSE}
p2_df = tibble(
  vec_numeric = rnorm (10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("A","B","C"), length=10),
  vec_factor = factor(rep(c("small","medium","large"), length=10))
)


```
